### 2020-08-10 tex/paper.tex
escrita das secao das simulacoes

\begin{center}
\section*{\centerline {A new family of continuous distributions: properties and applications}}
\vspace{0.3in}
{\large Gauss M. Cordeiro$^a$ and Maria do Carmo$^a$}\\
%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\
\end{center}

@@

\vspace{0.5in}
\noindent {\bf Key Words}: \\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$ Departamento de Estat\'{\i}stica, Universidade Federal de Pernambuco, Brazil.\\
e-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br} \\

>>>>

\begin{center}
\section*{\centerline {A new family of continuous distributions: properties and applications}}
\vspace{0.3in}
{\large Gauss M. Cordeiro$^a$ , Maria do Carmo$^a$ and Pedro Rafael D. Marinho$^b$}\\
%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\
\end{center}

@@

\vspace{0.5in}
\noindent {\bf Key Words}: \\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\
